Escape Analysis and Specialization in a Tracing JIT

### 2010-09-28 talk/pepm2011/paper.tex
list of benchmarks I want to use

>>>>

Benchmarks from the Computer Language Benchmark Game are: fannkuch, nbody,
meteor-contest, spectral-norm.

\textbf{crypto\_pyaes}: AES implementation.
\textbf{django}: The templating engine of the Django web
framework\footnote{\texttt{http://www.djangoproject.com/}}.
\textbf{go}: A Monte-Carlo Go
AI\footnote{\texttt{http://shed-skin.blogspot.com/2009/07/disco-elegant-python-go-player.html}}.
\textbf{html5lib}: HTML5 parser
\textbf{pyflate-fast}: BZ2 decoder
\textbf{raytrace-simple}: ray tracer
\textbf{richards}: The Richards benchmark \cite{XXX}
\textbf{spambayes}: A Bayesian spam filter\footnote{\texttt{http://spambayes.sourceforge.net/}}.
\textbf{telco}: A Python version of the Telco decimal
benchmark\footnote{\texttt{http://speleotrove.com/decimal/telco.html}}, using a pure
Python decimal floating point implementation.
\textbf{twisted\_names}: A DNS server benchmark using the Twisted networking
framework\footnote{\texttt{http://twistedmatrix.com/trac/}}.
